---
title: "import_wearlog"
author: "Carolina Guidolin"
date: "2024-06-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Note: run this script after import_LL

# Importing Wear log files 
Here, we import the raw data from the wear log

```{r}
filepath <- here("G:/cyepi/code/pre-processing/nonwear_detection/wearlog")

# Get the files names from directory
wearlogfiles = list.files(filepath, pattern="*.csv", full.names = TRUE)

```

## Coding of non-wear time according to the Wear log 
Here we create States (using import_Statechanges) that code for the 3 most important information contained in the Wear log:
1. When the light glasses were on,
2. When the light glasses were off,
3. When the light glasses were put off for sleep. 
Note: Retrospective and real-time information are treated as equal for this step. 
```{r pressure, echo=FALSE}
wearlog_entries_raw <- 
  #filenames:
  wearlogfiles %>% 
  #import_Statechanges from LightLogR to create states based on timestamps
  LightLogR::import_Statechanges(
    sep = ";", dec = ",", Datetime.format = "dmyHM", tz = "Europe/Berlin", 
    Id.colname = record_id,
    State.colnames = 
      c("wearlog_on", "wearlog_off", "wearlog_past_on", "wearlog_past_off", "wearlog_bed", "wearlog_past_sleep"),
    State.encoding = 
      c("1", "0", "1", "0", "2", "2") #off coded as 0, on coded as 1, sleep coded as 2
    ) 

```